---
title: "R Notebook"
output: html_notebook
---


```{r}
wb = read.csv("WorldBank.csv")
row.names(wb) = wb$Country.Name
wb_1 = wb[,c(13,14,16,17,25,33,42,43,44,52,53)]
wb.scale = scale(wb_1)
```

```{r, fig.width=15,fig.height=15}
wb.dist = dist(wb_1.na.scale, method = "euclidean")
wb.clust = hclust(wb.dist, method="ward.D")
plot(wb.clust)
```
```{r}
wb_1.na = na.omit(wb_1)
dim(wb_1.na)
wb_1.na.scale = scale(wb_1.na)
```

# The only things I can really pick out are that Cluster 4 is some of the most developed countries
# Also, it seems like Cluster 8 is grouped because it has mostly NA values (North Korea, Cuba)
# Clusters 8, 10 outliers (Cluster 10 just Sierra Leone and Yemen)?
# Mostly grouping by NA values I think :(
```{r}
country.grps = cutree(wb.clust, k=10)
clust.grps(wb_1.na,country.grps,parcoord=TRUE)
```

#Trying to get a random subset of the countries so it's more readable
# Cluster 1 is by far the largest - outliers throwing it off?? This group only has data for Telephone and PerInternet
# Throws off the groups a lot - United States/Canada/

```{r}
wb.sub <- wb_1[sample(1:nrow(wb_1),50,replace=FALSE),]
wb.sub.scale = scale(wb.sub)
wb.sub.dist = dist(wb.sub.scale, method = "euclidean")
wb.sub.clust = hclust(wb.sub.dist, method="ward.D")
plot(wb.sub.clust)
country.sub.grps = cutree(wb.sub.clust, k=10)
clust.grps(wb_1,country.sub.grps,parcoord=TRUE)
```


```{r}
library(corrplot)
wb_1.naomit = na.omit(wb_1)
WB.cor = cor(wb_1.naomit)
corrplot(WB.cor, tl.cex=.6)
corrplot(WB.cor,order="hclust", tl.cex=0.6)
```


```{r, fig.height=15, fig.width=15}
wb_1.pca = princomp(wb_1.naomit, cor=TRUE)
biplot(wb_1.pca, )
```

```{r}
wb_1.pca$loadings
wb_1.R = cor(wb_1.naomit)
wb_1.PCA = eigen(wb_1.R)
```

