---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

Row names are country names, omitted country names and country codes.

```{r, echo=FALSE}
e_wb = read.csv("worldbank.csv")
row.names(e_wb) = e_wb$Country.Code
e_wb = e_wb[,-c(1,2)]
```

```{r}
# Excluding variables with more than 6 missing values (Is there a more efficient way to do this than just counting 
# in summary view?)
e_wb_sub = e_wb[,-c(4,7,11,14,15,24,26)]
e_wb = na.omit(e_wb_sub)
```

Initial biplot - first 9 PCA values are > 1
```{r, fig.width=10, fig.height=10}
e_wb.pca = princomp(e_wb, cor=TRUE)
biplot(e_wb.pca, cex=.6)
#biplot(WB.pca, cex = .6, choices=3:4)
#e_wb.pca$loadings
```

Now I'm excluding Deathrate, Fertility rate, telephone, perforest, import value, importvolume, perinternet, permigrant, cellphones, trafficmortality, air pollution, pop0to14, perpopgrowth, ruralpopgrowth, secureservers, totaltaxrate, urbangrowth

```{r}
e_wb = e_wb[,-c(4,8,9,10,13,14,18,19,24,25,28,29,32,34,35,40,44)]
e_wb.pca = princomp(e_wb,cor=TRUE)

```

Now the first five are important.

```{r, fig.width=10, fig.height=10}
biplot(e_wb.pca, cex=.6)
```
It looks like my PCAs Comp. 1 and Comp. 2 are measures of life expectancy and employment, respectively.
Going to exclude some more redundant variables:

PerEmployedFemale/PerEmployedMale (because they will just be the opposite of unemployed m/f), FemaleSurvto65/Male, PerUrban

```{r}
e_wb = e_wb[,-c(5,6,22,23)]
e_wb.pca = princomp(e_wb,cor=TRUE)
```

```{r, fig.width=10, fig.height=10}
biplot(e_wb.pca, cex=.6)
```

Questions:
  1. How do I know what Comp1 and Comp2 are measuring/how they are weighting the variables when the data set is so big (computing eigenvectors lots of computation)
